Assessing paravascular transport in the parenchyma by partial differential equation (PDE) constrained optimization

### 2018-10-28 tex/paper.tex
Supplementary

\subsection{Verification in terms of the manufactured solution}
Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise, number of observations and time-resolution of the forward model. When presenting the results, we denote the relative error of the diffusion parameters as 
\begin{equation}
 D_{\Omega_i}\sp{rel} = \frac{D_{\Omega_i}\sp{found} -D_{\Omega_i}\sp{true} }{D_{\Omega_i}\sp{true} }, \text{ for } i=1,2,3
\end{equation}
For the boundary parameter $g$, the relative error norm is defined as 
\begin{equation}
|| g ||\sp{rel} = \frac{ \sum\limits_{t_j} || g_{found}(t_j) -g_{true}(t_j)||_{L^2(\Omega_1)} }{  \sum\limits_{t_j}||g_{true}(t_j)||_{L^2(\Omega_1)} }
\end{equation}
The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{TAB::timesteps}, Table~\ref{TAB::double} and Table~\ref{Tab::Noise0.3}

@@

In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations if $\alpha\gg\beta$ and the number of time-steps are much larger than the number of observations. For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observations. These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times. Further tests are documented in the Supplementary.

@@

\subsubsection{The noise susceptibility}
The MRI data contains noise, hence an investigation to the noise susceptibility is needed. This was done by pointwise adding uniform distributed noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations. Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$. Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
different noise levels with $\alpha=0.0001$,$\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
of noise shown in the upper rows.      
In Table~\ref{Tab::Noise0.3} the noise amplitude was set to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect. The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$. Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.

>>>>

\subsection{Verification in terms of the manufactured solution}
Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise, number of observations and time-resolution of the forward model. When presenting the results, we denote the relative error of the diffusion parameters as 
\begin{equation}
 D_{\Omega_i}\sp{rel} = \frac{D_{\Omega_i}\sp{found} -D_{\Omega_i}\sp{true} }{D_{\Omega_i}\sp{true} }, \text{ for } i=1,2,3
\end{equation}
For the boundary parameter $g$, the relative error norm is defined as 
\begin{equation}
|| g ||\sp{rel} = \frac{ \sum\limits_{t_j} || g_{found}(t_j) -g_{true}(t_j)||_{L^2(\Omega_1)} }{  \sum\limits_{t_j}||g_{true}(t_j)||_{L^2(\Omega_1)} }
\end{equation}
The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{Tab::Noise0.3}

@@

In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations if $\alpha\gg\beta$ and the number of time-steps are much larger than the number of observations. For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observations. These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times. 
Tests with variation in the number of timesteps and observations are documented in the Supplementary.

@@

\subsubsection{The noise susceptibility}
The MRI data contains noise, hence an investigation to the noise susceptibility is needed. This was done by pointwise adding uniform distributed noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations. Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$. Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
different noise levels with $\alpha=0.0001$,$\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
of noise shown in the upper rows.      
In Table~\ref{Tab::Noise0.3} the noise amplitude was set to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect. The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$. Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$. Results with noise  amplitudes at 0.03 are listed in the Supplementary.
